Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-19 article.tex
we use both filter in the final approach

As the first plot in Figure~\ref{fig:filtered-signal} illustrates, the raw
fluoresence signal is very noisy due to light scattering artifacts that
ordinarily affects the quality of the recording~\citep{lichtman2011big}.
Accordingly, the first step of our pipeline is to smoothen the signal, using a
low-pass filter for filtering out high frequency noise and resulting in the
second plot in the figure:
\begin{align}
% symmetrical median filter
f_1(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i \label{eq:symetric-median}, \\
% asymmetrical weighted median
f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i,
\label{eq:weighted-asymetric-median}
\end{align}
where $f_1$ is the filter proposed in the simplified variant of our approach
and $f_2$ is the filter actually used within our winning algorithm.

@@

Figure \ref{fig:curves} shows the ROC curve and precision-recall curve
for correlation, GTE and partial correlation on the \textit{normal-2}
dataset. The partial correlation outperforms other state-of-the-art methods
by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.05$ in
AUROC.

Two reasons might explain such overwhelming difference: (i) among
those methods only the partial correlation makes the distinction between
direct and indirect connections, (ii) the simulated network from the
\citep{stetter2012model} generator could be reduced to a linear model after
pre-processing. Those results is obviously generalized over the other
datasets see Appendix \textcolor{red}{REF}.

As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance
increases with deeper trees. The reason is twofold. First, the deeper the
tree, the larger is the conditioning. As it was observed in the comparison
between correlation and partial correlation, it screens indirect links in the
infered network. Second, the number of trees when trees are small need to be
much higher in order to correctly estimate all pairs. However, as suggested by
\cite{Gilles2014understanding}, limiting the maximal depth of trees may help
to reduce the misestimation bias in variable importance comuting, i.e.
infering the strengh of a link.

@@

\begin{figure}[bth]
\centering
\includegraphics[width=\linewidth]{images/curves}
\caption{Method precision-recall and roc curves. \textcolor{red}{GENI3?}
         $\tau=0.11$}
\label{fig:curves}
\end{figure}

@@

\begin{table}[tbh]
\centering
\small
\begin{tabular}{@{}l *{8}{c}@{}}
\hline
  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
\hline
Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
P                   & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
P + W               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
P + W + PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
%Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
\end{tabular}
\caption{TODO \textcolor{red}{version simple!!}}
\label{tab:tab3}
\end{table}

>>>>

As the first plot in Figure~\ref{fig:filtered-signal} illustrates, the raw
fluorescence signal is very noisy due to light scattering artifacts that
ordinarily affects the quality of the recording~\citep{lichtman2011big}.
Accordingly, the first step of our pipeline is to smoothen the signal, using
one the following low-pass filter for filtering out high frequency noise :
\begin{align}
% symmetrical median filter
f_1(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i \label{eq:symetric-median}, \\
% asymmetrical weighted median
f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i,
\label{eq:weighted-asymetric-median}
\end{align}
where \textcolor{red}{$f_?$} effect is shown in the second plot in the figure.

@@

Figure \ref{fig:curves} shows the ROC curve and precision-recall curve
for correlation, GTE and partial correlation on the \textcolor{red}{normal-?}
dataset. The partial correlation outperforms other state-of-the-art methods
by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.05$ in
AUROC.

Two reasons might explain such overwhelming difference: (i) among
those methods only the partial correlation makes the distinction between
direct and indirect connections, (ii) the simulated network from the
\citep{stetter2012model} generator could be reduced to a linear model after
pre-processing. \textcolor{red}{Those results generalized over the other
datasets see Appendix REF.}

\textcolor{red}{TODO: depth discussion }

@@

\begin{figure}[bth]
\centering
\includegraphics[width=0.6\linewidth]{images/curves}
\caption{Method precision-recall and roc curves. \textcolor{red}{GENI3?}
         $\tau=0.11$}
\label{fig:curves}
\end{figure}

@@

\begin{table}[tbh]
\centering
\begin{tabular}{@{}l *{8}{c}@{}}
\hline
  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
\hline
Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
P                   & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
P + W               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
P + W + PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
%Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
\end{tabular}
\caption{TODO \textcolor{red}{version simple!!}}
\label{tab:tab3}
\end{table}
